---
title: "Predict Miles per Gallon with Simple Regression Models"
author: "Ana Rita Silva"
date: "2023-01-16"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is part of Data Science Specialization on Coursera. It belongs to a peer-graded assignment: Shiny Application and Reproducible Pitch.

The materials used are from RStudio "mtcars" dataset.

To consult the code used to develop this application (server.R and ui.R): \<link.com\>

## mtcars Data

```{r}
data(mtcars)
head(mtcars)
```

## ui.R code

library(shiny)

shinyUI(
navbarPage("Developing Data Products Assignment",
tabPanel("Simple Regression",
(fluidPage(
titlePanel("Predict Miles per Gallon (mpg) with Simple Regression Models"),
sidebarLayout(
sidebarPanel(
selectInput("variable", "Select Input for Simple Regression",
c("am","cyl","hp","wt","disp","drat","qsec","gear","carb")),
checkboxInput("simple_model","show simple model",value=FALSE),
submitButton("Submit")

## server.R code

library(shiny)
library(ggplot2)
library(olsrr)
data(mtcars)

mtcars\$cyl \<- factor(mtcars\$cyl)
mtcars\$vs \<- factor(mtcars\$vs)
mtcars\$gear \<- factor(mtcars\$gear)
mtcars\$carb \<- factor(mtcars\$carb)
mtcars\$am \<- factor(mtcars\$am,labels=c("Automatic","Manual"))

shinyServer(function(input, output) {

full_model\<-lm(mpg \~ am+cyl+hp+wt+disp+hp+drat+qsec+gear+carb,data=mtcars)
best_model\<-lm(mpg \~ am+hp+wt+disp+qsec,data=mtcars)
